---
title: "Introduction to R Markdown"
author: "Tulika"
date: "14 March 2016"
output: word_document
---

In this document Google stock value from Jan01,2015 until yesterday 2016

For this purpose, we will use `tseries`  *Rpackage*. I will first load `tseries`  *Rpackage* into R environment.


```{r,warning=FALSE}
library(tseries)
```

Next, I will use the get.hist.quote() function to download the historical financial data from a given provider (Yahoo is the default).

```{r}

google.data = get.hist.quote(instrument = "goog"
                             ,start = "2015-01-01", 
                             end= "2016-03-13",
                             quote="AdjClose")

```


Next, I will like to get some summary statistics using the `summary()` function.

```{r}

goog.close = as.numeric(google.data$AdjClose)
summary_stat = summary(goog.close)

head(goog.close)
summary_stat
```

We can tabulate our summary as follows:

Min | 1st Quart | 2nd Quart | Mean | 3rd Quart | Max
----|-----------|-----------|------|-----------|----
`r summary_stat[1]` | `r summary_stat[2]` | `r summary_stat[3]` |`r summary_stat[4]` | `r summary_stat[5]`| `r summary_stat[6]` |

We can visualize our stocks data:

```{r,tidy=TRUE}
plot(google.data,
     xlab = "Time",
     ylab = "Google Stock Price")
```

# Sources

We have a list of many useful sources to learn R Markdown:

* [Rstudio](http://rmarkdown.rstudio.com/)
* [Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)

We can have number bullets:

#. hjgdash ds
#. ksjdlkd ks
#. hjdshga sh


     